\papertitle

### 2020-01-27 paper/paper.tex
Further modifications

Now:
\begin{enumerate}
  \item user runs Cylc to start a suite
  \item Cylc parses the suite file, generate dependencies and generate a schedule for the execution
  \item Once a task can be executed because dependencies are ready: Cylc generates on the fly a Slurm script with the required metadata for SLURM and invoking the user-defined script for that task and then runs Slurm to queue the script
  \item Slurm queues the task, and once the task is ready to be dispatched it is started on the supercomputer
  \item The shell-script executes the users-provided instructions, some of those are to generate file names using Cylc and the variables that are generated by Cylc. These filenames use templates provided by the user that defines the storage location to be used.
  \item User-specified applications run taking the filenames as instructed.
  The application may use NetCDF or XIOS to perform the I/O.

@@

Our Plan:

\begin{enumerate}
  \item user runs Cylc to start a suite.
  \item Cylc parses the suite file, generate dependencies and generate a schedule for the execution.

@@

  \item Once a task can be executed because dependencies are ready: Cylc generates on the fly a Slurm script with the required metadata for SLURM and invoking the user-defined script for that task.

@@

  \item Slurm queues the task, and once the task is ready to be dispatched it is started on the supercomputer

@@

  \item The shell-script executes the users-provided instructions, some of those are to generate file names using Cylc and the variables that are generated by Cylc.
  These filenames use templates provided by the user that defines the storage location to be used.

@@

  \item User-specified applications run taking the filenames as instructed.
    The application may use NetCDF, XIOS

    OR ESDM

    to perform the I/O.

@@

>>>>

\section{Stages}

\begin{figure}[H]
  \centering
  \includegraphics[scale=1.4]{stages}
  \caption{Stages}
  \label{fig:work2}
\end{figure}

Now.

  \item \textbf{Suite}\ \ The user runs Cylc to start a suite. The file \texttt{suite.rc} is created.

  \item \textbf{Cylc}\ \ Cylc parses the suite file, generate dependencies and defines a schedule for the execution.

  \item \textbf{Slurm}\ \ Once a task can be executed (dependencies are fulfiled), Cylc generates on the fly a Slurm script with the required metadata for Slurm, invokes the user-defined script for that task, and runs Slurm to queue the process.

  \item \textbf{Task}\ \ Once the task is ready to be dispatched by Slurm, it is started on the supercomputer.

  \item \textbf{Script}\ \ The shell-script executes the users-provided instructions allowing Cylc to generate its internal variables. To create the filenames, Cylc reads templates provided by the user that defines the storage location to be used.

  \item \textbf{Application}\ \ The user-specified application runs taking the filenames as instructed. The application may use NetCDF or XIOS to perform the I/O.

@@

Our Plan.

  \item \textbf{Suite}\ \ The user runs Cylc to start a suite. The file \texttt{suite.rc} is created.

  \item \textbf{Cylc}\ \ Cylc parses the suite file, generate dependencies and defines a schedule for the execution.

@@

  \item \textbf{Slurm}\ \ Once a task can be executed (dependencies are fulfiled), Cylc generates on the fly a Slurm script with the required metadata for Slurm, invokes the user-defined script for that task, and runs Slurm to queue the process.

@@

  \item \textbf{Task}\ \ Once the task is ready to be dispatched by Slurm, it is started on the supercomputer.

@@

  \item \textbf{Script}\ \ The shell-script executes the users-provided instructions allowing Cylc to generate its internal variables. To create the filenames, Cylc reads templates provided by the user that defines the storage location to be used.

@@

  \item \textbf{Application}\ \ The user-specified application runs taking the filenames as instructed. The application may use NetCDF or XIOS to perform the I/O.

  The application may use NetCDF, XIOS, or ESDM to perform the I/O.

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{workflow1-v2}
  \caption{Workflow 1.}
  \label{fig:work1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{workflow2-v2}
  \caption{Workflow 2.}
  \label{fig:work2}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{workflow-all}
  \caption{Workflow 2.}
  \label{fig:work2}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{cc}
  \includegraphics[scale=0.6]{workflow1-v2} &
  \includegraphics[scale=0.6]{workflow2-v2}
  \end{tabular}
  \caption{Workflows 1 and 2.}
  \label{fig:work1}
\end{table}
